% -*- Mode: latex -*-
\input{moves.tex}

\chead{\titlefont\Huge\textbf{The Basic Moves}}

\begin{document}
\begin{multicols}{3}

  \begin{move}
    When you \TRIGGER{impose your will} on someone, roll +Will. On a
    10+, they do what you want or they get the hell out of your
    way. On a 7-9, they may choose to instead:
    \begin{itemize}
      \setlength\itemsep{-.5em}
    \item Give you something they think you want or need
    \item Offer to help, at a cost
    \item Bunker down until this blows over
    \item Make themselves scarce
    \end{itemize}
\begin{movedetail}
  Impose Your Will is a move for when you are trying to force someone
  to act in a certain way, or to get out of your way. This could be by
  threatening them or something they care about. It could also be
  accomplished in a number of other ways, but the key part is that you
  are trying to force them to do something. Not coerce, not trick, not
  manipulate. Force. It has been noted that you can Pull One Over on
  the Consensus (or reality) but you can only Impose Your Will on a
  person. This is entirely intentional. Imposing Your Will on reality
  (or the Consensus) is an entirely different move. We call that Do
  Rending Magic.
\end{movedetail}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{assert your Paradigm over another Mage's}, roll
    +Charm (-1 if Tethered). On a 10+, hold 3, or on a 7-9, hold
    1. You can spend your hold 1 for 1 to:
    \begin{itemize}
      \setlength\itemsep{-.5em}
    \item Have them mark experience (if an NPC, they comply with a
      reasonable request)
    \item Give them a +1 or -1 on their next roll (if an NPC, enhance
      or counter their next use of magic)
    \item Cause their current Discord to backlash
    \end{itemize}
    On a miss, they hold 1 against you, on the same terms.
\begin{movedetail}
  For Mages, there isn't all that much hope of manipulating each other
  subtly. You can tell another mage what you want them to do, but when
  they also have reality-bending powers, there's rarely any way to
  guarantee they'll do what you want. That is, unless you're stronger
  than they are magically. That's where this move comes in. Mages, out
  of pragmatism, must operate on a hierarchical structure, which is to
  say that if another mage is magically superior to you, they have a
  measure of control over you. If you demonstrate your superiority
  over another mage, you're also showing them some of how you view the
  world, they understand you slightly better (or maybe slightly worse)
% Maybe rework this to include bits about leveraging your magical
% superiority into getting others to do what you want.
\end{movedetail}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{attempt to sway a non-Mage magical being},
    demonstrate your magical superiority and tell them what you
    want. Roll +Charm (-1 if Tethered). On a hit, they ask you to
    promise something first, and do it if you promise. On a 10+,
    whether you keep your promise is up to you, later. On a 7-9, they
    need some concrete assurance right now.
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{use a sleeper} for your own ends, you must first
    present something they want. Roll +Charm. On a success, they will
    do what you want. On a 10+, they will do what you want to the best
    of their abilities. On a 7-9, they need proof that they'll get
    what they want, or they need it before they'll do anything for
    you.
  \end{move}

  \columnbreak
    
  \begin{move}
    When you \TRIGGER{sell a lie} (to a person or to the Consensus),
    explain why they might believe it and roll +Wits. On a 10+, you've
    done it, with no-one the wiser. On a 7-9 you only mostly get away
    with it; the GM will offer you a hard bargain, worse outcome, or
    tough choice.
\begin{movedetail}
  This is one of the most complex moves in the game, and also one of
  the most versatile. Any time you're trying to slip something by a
  person in conversation, or otherwise trick them, this is the move to
  go to. Any time you try to slip a subtle, harmonious magical
  effect past the filters of reality, this is the move to go
  to. Pretty much any magic that doesn't fit into one of the other
  moves probably can fit into this one.
\end{movedetail}
  \end{move}

  \vspace{1em}
  
  \SEPARATOR

  \begin{move}
    When you \TRIGGER{outmaneuver, outpace, or outfox}, roll
    +Grace. On a 10+, you're scot free. On a 7-9, choose 2, or let
    the GM choose the worst 1:
    \begin{itemize}
      \setlength\itemsep{0em}
    \item You stumble, trip up, or falter
    \item You attract attention
    \item You have to leave something behind
    \item You leave an obvious trail
    \item You damage something
    \end{itemize}
\begin{movedetail}
  This move is particularly useful for when you're trying to do
  something quickly, or craftily. The GM might call for this move when
  you're trying to outpace a rogue mage in a foot-race, or when you're
  trying to avoid automagical countermeasures on that machine you just
  jacked yourself into. This move will save your bacon a hundred times
  over before you're done with it.
\end{movedetail}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{keep your head down} to avoid attention, roll
    +Wits. On a 10+, you avoid notice, suspicion, or detection. On a
    7-9, someone, but not everyone, notices you. Choose two:
    \begin{itemize}
      \setlength\itemsep{0em}
    \item They keep quiet about it
    \item They weren't actively looking for you
    \item They don't start to follow you
    \item They don't have backup
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{do Rending magic} and it affects a Lookout, gain
    2 Discord, Backlash, and roll +nothing (the Consensus doesn't care
    how smart or sexy you are).

    On a 10+ choose up to 3, on a 7-9 choose exactly 2.
    \begin{itemize}
      \setlength\itemsep{0em}
    \item You only gain 1 Discord
    \item You don't Backlash
    \item You don't cause collateral damage
    \item You don't draw extra attention
    \end{itemize}
    On a miss, choose one, but not ``You don't Backlash.''
  \end{move}

  \columnbreak
  
  \begin{move}
    When you \TRIGGER{exert yourself} physically on the world or another
    person, roll +Body. On a 10+, choose 3. On a 7-9, choose 2:
    \begin{itemize}
      \setlength\itemsep{0em}
    \item You accomplish your goal
    \item You aren't injured in the process
    \item You don't cause any collateral damage
    \item You impress or dismay the target or onlookers
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{Backlash}, roll +Discord, then reset Discord to
    0.

    On a 10+ choose 1:
    \begin{itemize}
      \setlength\itemsep{0em}
    \item You begin to see Discordant Visions
    \item You enter a Reality Fracture
    \item You are sucked into a Discordant Realm
    \end{itemize}

    On a 7-9, choose 2:
    \begin{itemize}
      \setlength\itemsep{0em}
    \item You take 3 Harm
    \item You don't reset your Discord to 0
    \item A Discordant Sign manifests
    \item A Consensus Enforcer manifests
    \end{itemize}

    On a miss, you shake it off with minimal lasting effects.
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{do magic that is Aligned to your Paradigm}, take
    +1 forwards when following up on that magic.
  \end{move}

  \SEPARATOR

  \begin{move}
    When you \TRIGGER{help or hinder} another PC, roll +Anchors. On a
    10+ they get a +1 or -2 to their roll, your choice. On a 7-9 they
    still get the bonus or penalty, but you open yourself to cost,
    danger, or retribution.
  \end{move}

\end{multicols}
\end{document}
