% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Hedge Mage}
\renewcommand{\Picture}{Hedge-Mage-new}
\renewcommand{\Description}{"Once Upon a Time, Humans could move mountains with their will. Now, it is upon us to carry on the ancient traditions, and master as many types of magic as we can."
}
\renewcommand{\Names}{Merle, Freya, Orenna, Benjamin, Liro, Norfeld, Wood, Sherand, Lilith, Melinda, Corin, Wilhelm, Byecross}
\renewcommand{\Trivialized}{{\small Because of my attitude, because I was neurodivergent, because I couldn't keep up, \BLANK}}
\renewcommand{\Questioned}{{\small Because of my detachment, because I don't want to fit in, because I screwed up, \BLANK}}
\renewcommand{\Hunted}{{\small For fun, for my Talents, because I disturb people, \BLANK}}

\renewcommand{\Eyes}{distracted eyes, glittering eyes, faraway eyes, inscrutable eyes, determined eyes}
\renewcommand{\Faces}{wizened face, deadpan face, vivacious face, brisk face, chipper face, sharp face}
\renewcommand{\Bodies}{spindly body, angular body, aggressive body, thickset body, dexterous body}
\renewcommand{\Clothes}{rustic clothes, embellished clothes, coarse clothes, domestic clothes}
\renewcommand{\Auras}{sprightly aura, stalwart aura, agile aura, musical aura, flashy aura, unrefined aura}

\renewcommand{\HomeAnchorItems}{
\item The Ancestral Family Home
\item  My cottage with a small garden out back
\item  My penthouse apartment that I barely afford
}
\renewcommand{\ConnectionAnchorItems}{
\item Lazarus, the man I saved from drowning
\item  My well-meaning mother
\item  Chance, my favorite nibbling
}
\renewcommand{\MemoryAnchorItems}{
\item : (pick one) My grandfather's old chipped pipe
\item  My compass that doesn't point north
\item  A leaf from the forests I knew from \BLANK
}
\renewcommand{\Gear}{
\item 1 Savings

\item Choose a symbol of hospitality: A set of fine china; A spare bedroom; A large cast-iron oven; The latest in home entertainment systems; A well stocked bar.

\item Choose a tool: A tablesaw and misc. woodworking equipment; A glassblowing oven; A well-used set of gardening implements; An emergency shotgun, loaded with rock-salt.

}
\renewcommand{\StatsSpaceAdjust}{2em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Without (max Without +2)
\item Gain +1 Within (max Within +2)
\item Gain +1 Entropy (max Entropy +2)
\item Pick a new Hedge Mage move
\item Pick a playbook move from another playbook
}
\renewcommand{\SpecialAdvancements}{
\item Pick a new Hedge Mage move
\item Pick a new Hedge Mage move
\item Pick a playbook move from another playbook
\item Pick a playbook move from another playbook
\item Gain +1 Dynamic (max Dynamic +3)
\item Get an Advanced Hedge Mage Move
}
\renewcommand{\MoveExplanation}{The Hedge Mage gets the \textbf{Exactly When I Mean To} move, and 2 other moves of your choice.}

\renewcommand{\MoveSpacing}{.5em}
\renewcommand{\Moves}{
  \DEFAULTMOVE{Exactly When I Mean To}{At the \TRIGGER{beginning of the session}, roll +Entropic. On a 10+, hold 2. On a 7–9, hold 1. At any time, either you or the MC can spend your hold to have you arrive in a scene, with the proper tools and knowledge, with or without any clear explanation why. Take +1 forward when you do so. On a miss, the MC holds 1, and can spend it to have you arrive, but somehow pinned, caught or trapped.}

\MOVE{Call Through Shadow}{When you \TRIGGER{call a mundane or common object to yourself}, roll +Dynamic. On a hit, you have successfully summoned it to you. On a 10+ you're in the clear. On a 7-9 choose 1:
\begin{itemize}
\setlength\itemsep{-.5em}
\item It comes out of an intense nearby situation
\item It comes with strings attached
\item It can be traced back to you.\end{itemize}}

\MOVE{Scrying Bowl}{When you have an object related to a person and use it to \TRIGGER{gaze upon their current situation}, roll +Without. On a 10+ all 3, on a 7-9 choose 1:
\begin{itemize}
\setlength\itemsep{-.5em}
\item They don't know they're being watched
\item You can identify where they are
\item You can discern what they are doing.\end{itemize}}

\MOVE{If You Ask Me}{When you \TRIGGER{offer an alternative perspective on someone's Paradigm}, roll +Without. On a hit, they gain experience. On a 10+, give them a new Aligned related to what you told them until the end of session.}

\MOVE{Magical Experimentation}{When you collaborate with other Mages to \TRIGGER{push your magic past its current boundaries} in a controlled setting, roll +Dynamic. On a 10+ all 3, on a 7-9 choose 1:
\begin{itemize}
\setlength\itemsep{-.5em}
\item It works pretty much as intended
\item It doesn't cause a scene, draw extra attention, or harm you
\item It was controlled enough that you can repeat it.\end{itemize}}

\MOVE{This One Is Mine}{When you \TRIGGER{call out another magical being}, so long as your companions don't interfere, others will give you enough space to finish it, come what may.}

}
\renewcommand{\SpecialMoveSpacing}{0em}
\renewcommand{\SpecialMove}{they gain one hold, which they can spend to cause you to appear as if by Exactly When I Mean To.}
\renewcommand{\Paradigms}{
  \PARADIGM{A Thousand Arcane Secrets}{Cantrips, Ritual Maigc  }{(choose one) Large-reaching effects, immediate effects  }{**Restrictions:** None}
		   
  \PARADIGM{Double, Double, Toil and Trouble}{Any type of effect  }{Magic that doesn't require preparation  }{**Restrictions:** (choose one) Preparation demands input from a knowledgable source, I require components of appropriate power.}
		   
}
\renewcommand{\PaneSix}{\Description

\GearSection}

\vspace {5em}

\begin{document}

\PLAYBOOK

\end{document}