% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Inspired By Pot}
%\renewcommand{\Picture}{}
\renewcommand{\Description}{Many people wonder where inspiration comes
  from. That question is boring to you, you know the answer. The right
  question is, how much can you do with that inspiration?}
\renewcommand{\Names}{Esin, Tobias, Tafari, Sameal, Mab, Fiona, Kai,
  Kendall, Flower, Ida, }

\renewcommand{\Eyes}{Burning eyes, dull eyes, hungry eyes, }
\renewcommand{\Faces}{Slack face, haggard face, shining face, stubborn
  face, yearning face}
\renewcommand{\Bodies}{Wiry body, full body, misshapen body}
\renewcommand{\Clothes}{Flowing clothes, fancy clothes, rags, hip
  clothes, active clothes, }
\renewcommand{\Auras}{Expansive aura, sucking aura, insinuating aura,
  kaleidoscope aura, tantalizing aura, }

\renewcommand{\Stats}{
Will +0, Wits -1, Charm +1, Grace +2, Body +1

Will +0, Wits +0, Charm +2, Grace +1, Body +0

Will +0, Wits +0, Charm +0, Grace +1, Body +2

Will +0, Wits +1, Charm +0, Grace +2, Body +0

}
\renewcommand{\AnchorNumber}{3}
\renewcommand{\Anchors}{
\item Neon and Crystal, some kids I hang out with on the weekend
\item Leslie, who cares about me but just doesn't understand
\item My last gift from \BLANK before they left
\item The diamond necklace from \BLANK
\item \BLANK, my greatest confidante 
\item The well-worn T-shirt I always sleep in
}
\renewcommand{\Secrets}{
\item \BLANK introduced me to my source (tell them +2)
\item \BLANK looks down on my attachment to my source (tell them -1)
\item I met \BLANK thanks to my source (tell them +1)
}
\renewcommand{\StatsSpace}{14em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Charm (max Charm +2)
\item Gain +1 Grace (max Grace +2)
\item Gain +1 Body (max Body +2)
\item Pick a new Inspired move
}
\renewcommand{\SpecialAdvancements}{
\item Pick a new Inspired move
\item Pick a playbook move from another playbook
\item Gain +1 Charm (max Charm +3)
\item Gain +1 Grace (max Grace +3)
\item Get an Advanced Inspired Move
}
\renewcommand{\MoveExplanation}{The Inspired gets the \textbf{Source}
  move, and 2 other moves of your choice.}
\renewcommand{\MoveSpacing}{0em}
\renewcommand{\Moves}{
\DEFAULTMOVE{Source}{You've identified the source of your inspiration,
  and it lifts you up. Take +1 ongoing while your source is present.}

\MOVE{Just When I Think You're Gone}{When you \textbf{pass up an
    opportunity to interact with your Source of Inspiration}, roll
  +Grace. On a hit, hold 1. On a 10+ you may spend your hold 1 for 1
  to have your source appear in the scene with no explanation
  needed. On a 7-9 you may spend your hold for the same, but your
  Source is threatened, captured, or in peril.}

\MOVE{Open Their Mind}{When you \textbf{introduce an individual to
    your Source to open their mind}, roll +Charm. On a 10+, they are
  not a witness the next time they would be for your magic. On a 7-9,
  you take +1 forward with them. On a 6-, in addition to whatever else
  the GM says, choose one:
  \begin{itemize}
    \setlength\itemsep{-.5em}
  \item They find they have a strong aversion to your Source
  \item They wish to take your Source away from you.
  \end{itemize}
}

\MOVE{Opiate for the Masses}{When you \textbf{bring your Source to a
    mob}, roll +Grace. On a 10+, hold 3. On a 7-9, hold 1. Spend your
  hold 1-for-1 to:
  \begin{itemize}
    \setlength\itemsep{-.5em}
  \item Discover a truth that they know
  \item Obtain something of value or use
  \item Get them to believe a truth
  \item Learn their potential
  \item Placate them and return them to their mundane lives
  \end{itemize}
}

\MOVE{Visions of Fate}{When you \textbf{jump into the havoc surging
    around you}, roll +Body. On a 10+, choose someone who pulls
  through, and someone who doesn't. On a 7-9, choose someone who pulls
  through OR someone who doesn't. Don't name a PC; name NPCs only. The
  GM will make your prediction come true, if it's even remotely
  possible. On a miss, take -1 ongoing until the havoc subsides.}

}
\renewcommand{\Paradigms}{
\PARADIGM{I Bend the Rules through my Source}{Mental magic,
  Time-Affecting magic}{Choose one: Magic that reinforces the status
  quo, Magic that doesn’t Protect my Source}{Choose this one: Magic
  without my Source}

\PARADIGM{My Source Lets me See the True Nature of
  Things}{Divinations, Transmutations}{Choose one: Obscuring magic,
  Changing thing that are Static}{Magic without my Source, Magic while
  Blind}
}

\renewcommand{\PaneSix}{\Description

  \SECTION{Your Source:}

  First pick your source's form: a person, an object, a substance, an
  abstract concept, an action, an emotion

  Next choose one of these: 
\begin{itemize}
\item Your source can be carried with you (+portable)
\item Your source is protected (+safe)
\item Your source is socially acceptable (+available)
\item Your source makes you more alert (+sharp)
\item Your source makes you more Aware (+magicsense)
\item Your source makes you feel more alive (+invigorating)
\item Your source helps you talk to people (+social)
\end{itemize}
  
And choose two of these: 
\begin{itemize}
\item You crave more and more of the source, your desire for it is
  insatiable. (+addictive)
\item Your source is rare or hard to find. (+rare)
\item Your source is short-lived (+quick)
\item Your source often harms you (+dangerous)
\item Your source is against the law (+illegal)
\item Your source attracts unwanted attention (+disruptive)
\item Your source makes your magic more unpredictable (+chaotic)
\end{itemize}
}
  
\begin{document}

\PLAYBOOK

\end{document}
