\documentclass[letterpaper,10pt]{article}
\setlength{\topmargin}{-1in}
\setlength{\textheight}{10in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{7in}

\setcounter{secnumdepth}{-1}

\usepackage{multicol}
\usepackage{fontspec}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{comment}

\pagenumbering{gobble}

\setmainfont [Path = fonts/,
  UprightFont = Aller_Rg.ttf,
  BoldFont = Aller_Bd.ttf,
  ItalicFont = Aller_It.ttf
]{Aller}
\newfontfamily\titlefont [Path = fonts/,
  UprightFont = Kingthings_Printingkit.ttf,
]{Kingthings}

\setlength\parindent{0pt}

\newenvironment{move}{}{}
\excludecomment{movedetail}
\newcommand{\TRIGGER}[1]{\textbf{#1}}
\newcommand{\SEPARATOR}{\vspace{-1em}\begin{center}\noindent\rule{6cm}{2pt}\end{center}}

\newcommand{\TITLE}[1]{\begin{center}{\titlefont\Huge\textbf{#1}}\end{center}}
\newcommand{\SECTION}[1]{\vspace{.5em}{\noindent\titlefont\LARGE\textbf{#1}}

}

\begin{document}

\TITLE{Living Moves and Savings}

\begin{multicols}{2}

\begin{move}
  If you are \TRIGGER{living below your means}, the first time during
  a session you spend some time at home, take 1 Harm (ignoring
  Preparations), gain +1 Savings, and roll +Body. On a 10+, nothing
  else happens. On a 7-9, choose one. On a 6-, choose two plus
  whatever the MC says.
  \begin{itemize}
  \item Something goes wrong with your home and it won't provide
    shelter until fixed
  \item You attract unwanted attention
  \item You irrevocably lose a valuable possession
  \item Unsavoury types and bad conditions get to you. Take 1
    additional Harm, also ignoring Preparations.
  \end{itemize}
\end{move}

\bigskip

\begin{move}
  If you are \TRIGGER{living within your means}, the first time during
  a session you spend some time at home, roll +Wits. On a 10+, all
  3. On a 7-9, choose 2. On a 6-, choose 1, and the MC makes a move.
  \begin{itemize}
  \item Your home isn't being actively targeted at the moment
  \item Your home is serene and restful, recover 1 Harm
  \item Nothing important has gone ``strangely missing'' in the last
    little while
  \end{itemize}
\end{move}

\bigskip

\begin{move}
  If you are \TRIGGER{living above your means}, the first time during
  a session you spend some time at home, roll +Charm, and pay 1
  Savings. On a 10+ both, on a 7-9 choose 1. On a 6-, pay an extra 1
  Savings and the MC makes a move
  \begin{itemize}
    \item Your money/lifestyle counts as something a Sleeper wants
      when Using a Sleeper
    \item Your home is secure and doesn't require extra attention from
      you to remain that way
  \end{itemize}
\end{move}

\vspace{30em}

\filbreak

When you buy something, it's generally of a quality appropriate for a
person of your means.

\SECTION{Sample prices, in Savings:}

\bigskip

1 - A nice meal for two. A suit. A thoughtful gift. An interstate
train ticket. A good psychic reading.

\medskip

2 - An ostentatious meal for two. A domestic plane ticket. A
handgun. A computer. A night's stay at a hotel. A rare book. Walk-in
medical treatment.

\medskip

3 - A short hospital stay. A college course. A short vacation. A
custom-crafted sword, made by a skilled Craftsperson.

\medskip

4 - A car, a motorcycle, a boat.

\medskip

\SECTION{Other Savings Rules}

\medskip

If at any point you are told you must pay a Savings and you cannot,
the MC makes a hard move.

\medskip

Once an in-game month, pay 1 Savings, or you are unable to meet your
expenses (and the MC makes a hard move).

\end{multicols}
\end{document}
