% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Mentor}
\renewcommand{\Picture}{mentor}
\renewcommand{\Description}{The secrets of the Universe are yours, but you don't guard them jealously. You share the wisdom with the precious few who will listen, taking on pupils who will one day surpass you.
}
\renewcommand{\Names}{Johan, Master Lu, Mina, Zoe, Indra, Roy, Puteri, Madame Leena, Marshki, Luce, Goswami, Sena}
\renewcommand{\Trivialized}{Because I was poor, because I was neurodivergent, because of my transgressions, \BLANK}
\renewcommand{\Questioned}{Because I see things as they really are, because I make my own path, because people started noticing me, \BLANK}
\renewcommand{\Hunted}{Because I'm famous, for my forbidden knowledge, so my students are not, \BLANK}

\renewcommand{\Eyes}{shining eyes, sunken eyes, alert eyes, glowing eyes}
\renewcommand{\Faces}{weathered face, gaunt face, wrinkled face, caring face, creased face}
\renewcommand{\Bodies}{wiry body, ripped body, lanky body \BLANK}
\renewcommand{\Clothes}{street clothes, flowing clothes, concealing clothes}
\renewcommand{\Auras}{menacing aura, peaceful aura, green aura, golden aura, fading aura, grounded aura, rippling aura}

\renewcommand{\HomeAnchorItems}{
\item The apartment I share with a few roommates
\item  My small but immaculate house downtown
\item  A single room at the back of my place of work
}
\renewcommand{\ConnectionAnchorItems}{
\item My best friend Ayah
\item  Devon, my oldest rival
\item  Zorrah, my forbidden love
}
\renewcommand{\MemoryAnchorItems}{
\item : (pick one) A portrait of my own long-dead mentor
\item  The gold necklace given to me by \BLANK
\item  A coal to remind me of \BLANK
}
\renewcommand{\Gear}{
\item No major possessions to speak of, but 3 Savings tucked away for a rainy day.

}
\renewcommand{\GearDirection}{No major possessions to speak of, but 3 Savings tucked away for a rainy day.
}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Entropic (Maximum Entropic +3)
\item Gain +1 Within (Maximum Within +3)
\item Gain +1 Static (Maximum Static +2)
\item Gain +1 Dynamic (Maximum Dynamic +2)
\item Get a new Mentor move
}
\renewcommand{\SpecialAdvancements}{
\item Get a new Mentor move
\item Choose a new option for your Students
\item Choose a new option for your Students
\item Choose a new option for your Place of Power
\item Get a playbook move from another book
\item Get a playbook move from another book
\item Get an Advanced Mentor Move
}
\renewcommand{\MoveExplanation}{The Mentor gets the \textbf{Pupils} move, and 2 other moves of your choice.}

\renewcommand{\Moves}{
  \DEFAULTMOVE{Pupils}{You have a number of students who follow your paradgimatic teachings. At the beginning of the session, roll +learning to determine how their studies are progressing. On a 10+ they have a surplus. On a 7-9, both a surplus and a want. On a 6-, they will do everything in their power to satisfy all their wants.\TRIGGER{}}

  

\MOVE{Meditation}{When you meditate on the best course of action for considerable time, roll +Dynamic. On a 10+ hold 3, on a 7-9 hold 1. You may spend this hold 1-for-1 at any time to ask the MC a question from this list, the MC will answer truthfully.  \TRIGGER{}
\begin{itemize}
\item u take +1 forward when acting on this information.
\item What's my escape route?
\item What are the unknowable risks?
\item Where can the Consensus be bent in my favor?
\item Who is favorable towards my plan?\end{itemize}}

\MOVE{Academe}{You have a Place of Power where you train your students. While you are within your Place of Power, take +1 forward to any Static rolls you make.\TRIGGER{}}

\MOVE{Matter over Mind}{You may roll +Static instead of +Without when impressing a lusus naturae in order to sway them.\TRIGGER{}}

\MOVE{What you Need, not what you Want}{When another character comes to you for advice and you tell them honestly what you think the best course of action is, they take +1 ongoing while following your advice, and you mark experience.\TRIGGER{}}

}

\renewcommand{\SpecialMoveSpacing}{10em}
\renewcommand{\SpecialMove}{they may immediately gain an Anchor (They still may not have more anchors than their playbook started with this way).}

\renewcommand{\Paradigms}{
  \PARADIGM{Your Focus Determines Your Reality}{Calming Magic, Projecting Power, Perfect Positioning  }\
  
           {(choose one) Breaking cycles, My magic must remain internal  }\
		   
           {(choose one) Technomagic, Magic while distracted}
		   
  \PARADIGM{I am the Platonic Ideal of Myself}{Static Magic, Convergence, Reflexive Magic  }\
  
           {(choose one) Fragmenting magic, creation, my magic cannot hide me  }\
		   
           {(choose one) Cynical magic, magic without conviction}
		   

\ParadigmBlanks
}

\renewcommand{\PaneFive}{\SECTION{Your Students:}
By default you have about 10 students, they are moderately studious sleepers and they respect you, though they're not fully loyal. They have their own lives apart from you, family and friends in the area. (learning +1. surplus: time. want:


departure.)

  \begin{itemize}
  \item Pick up to two of these:

  \item - Your students are competitive (replace want: departure with want: competition)

  \item - Your students are driven (replace surplus: time with surplus: dedication)

  \item - Your students are enthusiastic (replace surplus: time with surplus: energy)

  \end{itemize}

- Your students are lazy (replace want: departure with want: sloth)

  \begin{itemize}
  \item And one of these:

  \item - Your school is famous (add surplus: growth and want: infamy)

  \item - Your school is large (default students 20)

  \item - Your students are quick learners (+1 learning)

  \item - You have a protege; your most advanced student is Awakened

  \end{itemize}
}

\renewcommand{\PaneSix}{\Description

  \SECTION{Place of Power:}
  
  First, pick a facade:	
  \begin{itemize}
  \item Dojo
  \item Dance Studio
  \item Abandoned warehouse
  \item Stunt filming location
  \item Lecture hall
  \end{itemize}
    
  Then pick up to 1 Strength: 
+hidden, 
+famous, 
+easily defended,


  Pick at least 1 Weakness: 
+cramped, 
+dangerous, 
+temporary,


  A Ritual performed here will never (choose 1):
  \begin{itemize}
  \item Need help from an outside source
  \item Take longer than expected
  \item Have greater than intended effec
  \end{itemize}

  \SECTION{Paradigm List:}

  \Paradigms
}

\begin{document}

\PLAYBOOK

\end{document}