% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Pious}
%\renewcommand{\Picture}{}
\renewcommand{\Description}{You know the true meaning of sacrifice. It
  isn’t something dramatic or grandiose, sometimes it just means going
  without sleep so you can stake out the fields that cows keep
  disappearing from. There’s Something Larger than just you, and
  choosing that over your own needs, that’s sacrifice.}
\renewcommand{\Names}{Joan, Ether, Miranda, Brother Wilhelm, Francis,
  Emira, Marja, Ingrid, Bernard, Rishi, Sister Eliza}
\renewcommand{\Eyes}{caring eyes, quiet eyes, intense eyes, small
  eyes, inspired eyes, hard eyes}
\renewcommand{\Faces}{youthful face, lined face, sharp face, round
  face, marred face, open face}
\renewcommand{\Bodies}{hard body, sallow body, frail body, \BLANK}
\renewcommand{\Clothes}{orderly clothes, homespun clothes,
  conservative clothes, starched clothes}
\renewcommand{\Auras}{peaceful aura, driven aura, flowing aura,
  tight-fitting aura, hidden aura}
\renewcommand{\Stats}{
Will +0, Wits +0, Charm +2, Grace +0, Body +1

Will +0, Wits +1, Charm +2, Grace -1, Body +1 

Will +0, Wits +0, Charm +1, Grace +1, Body +1

Will +1, Wits +1, Charm +2, Grace +0, Body -1

}
\renewcommand{\AnchorNumber}{3}
\renewcommand{\Anchors}{
\item Kell, my heart’s delight
\item My wooden rose, a gift from my first love
\item My widowed sister-in-law 
\item My community
\item My dog-eared holy text
}
\renewcommand{\Secrets}{
\item I know \BLANK's second-biggest secret. (Tell them +1)
\item I trust \BLANK to guide the sleepers. (Tell them +1)
\item \BLANK does not fit into my vision of an Awakened Future (Tell
  them -2)
}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Charm (Maximum Charm +3)
\item Gain +1 Grace (Maximum Grace +2)
\item Gain +1 Will (Maximum Will +2)
\item Gain +1 Wits (Maximum Wits +2)
\item Get a new Pious move
}
\renewcommand{\SpecialAdvancements}{
\item Get a new Pious move
\item Get a new Pious move
\item Choose a new option for your Place of Power
\item Choose a new option for your Place of Power
\item Get a playbook move from another book
\item Get a playbook move from another book
\item Get an Advanced Pious Move
}
\renewcommand{\MoveExplanation}{The Pious gets the \textbf{Vows} move,
and 2 other moves of your choice.}
\renewcommand{\Moves}{
  \setlength\itemsep{-.25em}
  \DEFAULTMOVE{Vows}{When you \textbf{Eschew Mortal Comfort to Further
    your Goal}, roll +Charm. On a 10+ hold 3, on a 7-9 hold 1. Spend
  your hold 1-for-1 to declare someone involved in a situation owes
  you a small favor for past help.}
\MOVE{Listen to the Celestial Chorus}{When you tune in to the voices
  of the universe, sometimes they will have something helpful to
  say. Roll +Charm. On a hit you may ask questions from the below
  list, the GM will answer truthfully. On a 10+ ask 3, on a 7-9 ask 1.
  \begin{itemize}
    \setlength\itemsep{-.5em}
    \item Who here has the most potential? 
    \item Who can I trust? 
    \item What am I not seeing? 
    \item Who is telling the truth?
  \end{itemize}
}
\MOVE{Sanctuary}{You have access to a Place of Power, a safe haven
  against things that would harm servants of your Path.}
\MOVE{Last Rites}{You may always Assist someone on their death move,
  take +1 forward when doing so, and if you are successful, you both
  gain +1 secrets with each other.}
\MOVE{Exorcism}{When you attempt to \textbf{Banish a Controlling
    Spirit} roll +Body. On a 10+ choose 1, on a 7-9 choose 2:
  \begin{itemize}
    \setlength\itemsep{-.5em}
  \item You expose yourself to possession 
  \item The spirit is not afraid to come back 
  \item The controlled entity is harmed
  \end{itemize}
}
\MOVE{Holy Avenger}{You have a weapon, enchanted and attuned to your
  beliefs. When you \textbf{exert yourself physically} through it,
  roll +Body. On a hit, you may incapacitate or kill any one opponent
  on the battlefield. On a 7-9, they have a chance to react first, but
  can’t stop you. On a 6-, they were prepared. Sucks to be you.
}
}
\renewcommand{\Paradigms}{
  \PARADIGM{All is One and the One is All}{Pattern Magic, Cooperative Magic, Creation}\
           {Choose one: Selfish magic, Magic that divides}\
           {Choose one: Magic without Faith, Magic that doesn't involve people}

           \PARADIGM{I am the New Prophet}{Visions of the Future, Forging a Destiny}\
                    {Choose one: Things at Rest, Abjuration}\
                    
           {Choose one: Changing the Future you Know, Hiding the
             Truth}
}

\renewcommand{\PaneSix}{\Description

  \SECTION{Place of Power:}
  
  First, pick a facade: 	
  \begin{itemize}
  \item Place of Worship
  \item Forested Grove
  \item Basement Laboratory
  \item Old Log Cabin
  \item Wishing Well
  \item Ancestral Mausoleum
  \item Natural Spring 
  \end{itemize}
    
  Then pick up to 1 Strength:  +warded, +accorded ground, +famous,
  +private, +unique, +awakened spirit

  Pick at least 1 Weakness:  +inaccessable, +obvious, +public,
  +tainted +exposed, +business hours, +cramped

  A Ritual performed here will never (choose 1):
  \begin{itemize}
  \item Need a certain object 
  \item Cause everyone involved to Backlash
  \item Need extra time
  \end{itemize}
}

\begin{document}

\PLAYBOOK

\end{document}
