% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Primordial}
\renewcommand{\Picture}{Primordial-new}
\renewcommand{\Description}{You don't need fancy rituals, long drawn-out methods, or anything like that when you're working with the raw forces that shaped the Universe. That's what magic is really about.
}
\renewcommand{\Names}{Markus, Zakiel, Kassandra, The Hooded One, Crystal, Zuri, Malaki, Jeyde, Andrzej, Kolden, Sheth}
\renewcommand{\Trivialized}{Because of my anger, because the world isn't accessible, because of my fear, \BLANK}
\renewcommand{\Questioned}{Because I'm too different, because I can't stay still, because I'm afraid, \BLANK}
\renewcommand{\Hunted}{Because I hurt people, for my wealth, because I want to be, \BLANK}

\renewcommand{\Eyes}{burning eyes, dead eyes, piercing eyes, hungry eyes, hopeful eyes, white eyes}
\renewcommand{\Faces}{scarred face, drawn face, sallow face, eager face, tired face, weathered face}
\renewcommand{\Bodies}{imposing body, sinewy body, impish body, emaciated body, thickset body \BLANK}
\renewcommand{\Clothes}{concealing clothes, goth clothes, simple clothes, worn clothes, grubby clothes}
\renewcommand{\Auras}{fiery aura, dark aura, shifting aura, grey aura, brilliant aura, mossy aura}

\renewcommand{\HomeAnchorItems}{
\item A small tent down under the East Side Bridge
\item  My small house, where my pets live
\item  An apartment roughly the size of a closet
}
\renewcommand{\ConnectionAnchorItems}{
\item Agnes, my faltering grandmother
\item  Red, my oddball neighbor
}
\renewcommand{\MemoryAnchorItems}{
\item \BLANK from my childhood home
\item  The engraved knife I found in \BLANK
\item  The yellowed love letters my parents exchanged
}
\renewcommand{\Gear}{
\item Savings

\item Choose a prize that you won: An always-sharp knife; A large rainstick that sometimes works; A gold-plated hip-flask; A once-used guitar; An embellished leather jacket; A bleached animal skull.

\item Choose an impracticality: A large ornate mirror; Two sets black-tie attire; A high-powered telescope; A timeshare in the Hamptons; A 96" plasma TV; A marble bust of your head.

}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Without (Maximum Without +1)
\item Gain +1 Within (Maximum Within +2)
\item Gain +1 Static (Maximum Static +3)
\item Gain +1 Dynamic (Maximum Dynamic +2)
\item Get a new Primordial move
}
\renewcommand{\SpecialAdvancements}{
\item Get a new Primordial move
\item Get a second use of Serendipity
\item Get a playbook move from another book
\item Get a playbook move from another book
\item Get an Advanced Primordial move
}
\renewcommand{\StatsSpaceAdjust}{3em}
\renewcommand{\MoveExplanation}{The Primordial getsthe \textbf{
Strong Avatar}
move, 
the \textbf{
What Doesn't Kill You}
move, 
and 1 other move of your choice.}
\renewcommand{\MoveSpacing}{2em}
\renewcommand{\Moves}{
  \DEFAULTMOVE{Strong Avatar}{When you \TRIGGER{assert your Paradigm's truth to another Mage}, roll +Static. On a hit, replace one of their Opposed with one of your own for the rest of the scene. On a 10+, both mark experience.}
  \DEFAULTMOVE{What Doesn't Kill You}{The first time during a session your Health hits Code 30, mark experience.\TRIGGER{}}

\MOVE{Harvest}{When you \TRIGGER{Rip the Power from a Being}, describe what power and roll +Entropic. On a 10+ choose 3, on a 7-9 choose 1.
\begin{itemize}
\setlength\itemsep{-.5em}
\item It dies then and there.
\item You are empowered, take +1 ongoing until you fail a roll.
\item The power is not tainted.
\item You don't draw excessive attention.\end{itemize}}

\MOVE{Hunter}{When you \TRIGGER{track your Prey's magical trail} roll +Without. On a 10+ you find them, and they're close. On a 7-9, choose 1:
\begin{itemize}
\setlength\itemsep{-.5em}
\item You're in for a trek, but at least the trail is strong
\item They're close by, but the trail went cold\end{itemize}}

\MOVE{Serendipity}{Once per session, when you \TRIGGER{Use Magic to Fix it}, you may choose none of the options.}

}


\renewcommand{\SpecialMoveSpacing}{10em}
\renewcommand{\SpecialMove}{you each hold 1. You can each spend that hold at any time to Help or Hinder each other, no matter the barriers or distance between you.}

\renewcommand{\Paradigms}{
  \PARADIGM{Blood is the Strongest Sympathy}{Healing, Curses, Sympathy  }\
  
           {(choose one) Restoration, Mind-affecting magic  }\
		   
           {Magic that doesn't require sacrifice}
		   
  \PARADIGM{The World's Energy is Wrapped in Crude Matter}{Transformations and Transmutations, Energy Manipulation  }\
  
           {(choose one) Destruction, Creation  }\
		   
           {(choose one) Subtle magic, finesse magic}
		   
  \PARADIGM{I See, Hear, and Command the Spirits}{Elemental magic, Summoning  }\
  
           {(choose one) Man-made things, Transmutation  }\
		   
           {(choose one) Magic that disrespects the spirit world, magic without spirits}
		   
}
\renewcommand{\PaneSix}{\Description

\GearSection
}
\begin{document}

\PLAYBOOK

\end{document}