% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Voiced}
\renewcommand{\Picture}{Voiced-new}
\renewcommand{\Description}{{\itshape I am the voice of the past that will always be  
I am the voice of your hunger and pain  
I am the voice of the future  
I am the voice, I will remain
}}
\renewcommand{\Names}{Arin, Malak, Liron, Shir, Piper, Lark, Jaron, Calliope, Diona,}
\renewcommand{\Trivialized}{Because I spoke differently, because they thought I was broken, because of my looks, \BLANK}
\renewcommand{\Questioned}{Because I don't want to fit in, because I can't stay still, because of my friends, \BLANK}
\renewcommand{\Hunted}{For my talents, because I'm famous, because I appear broken, \BLANK}

\renewcommand{\Eyes}{glimmering eyes, vibrant eyes, piercing eyes, innocent eyes}
\renewcommand{\Faces}{open face, laughing face, pained face, serene face, fake face}
\renewcommand{\Bodies}{young body, burly body, tantalizing body, inconspicuous body, flashy body \BLANK}
\renewcommand{\Clothes}{crisp clothes, respectable clothes, stylish clothes, custom clothes, ill-fitting clothes}
\renewcommand{\Auras}{forbidden aura, enticing aura, waifish aura, vivid aura, purple aura}

\renewcommand{\HomeAnchorItems}{
\item A studio in the nice part of town that I sweet-talked my way into
\item  My spotless but lived-in condo
\item  A nice house in the bad part of town
}
\renewcommand{\ConnectionAnchorItems}{
\item \BLANK who is always there for me
\item  Allison, who taught me how to live
\item  \BLANK, who finishes my duets
}
\renewcommand{\MemoryAnchorItems}{
\item : (pick one) The long-dead bouquet of flowers I was given for \BLANK
\item  The headphones that \BLANK got for me
\item  The \BLANK my mother brought back from a business trip.
}
\renewcommand{\Gear}{
\item 1 Savings

\item An old police scanner to stay informed.

\item Choose a method of expression: A well-cared for musical instrument; A high end camera; A reliable sewing machine; A potter’s wheel and kiln; A small leased art studio; A waterproof notebook; A pirate radio station with a range of a mile or two.

\item Choose a way of protecting your voice: A large supply of herbal teas and tinctures; A small switchblade; A tube of pepper spray; A bullhorn.

}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Get +1 Static (Max Static +2)
\item Get +1 Dynamic (Max Dynamic +2)
\item Get +1 Within (Max Within +2)
\item Get +1 Entropic (Max Entropic +2)
\item Get a new Voiced move
}
\renewcommand{\SpecialAdvancements}{
\item Get +1 Without (Max Without +3)
\item Get +1 Static (Max Static +3)
\item Get a new Voiced move
\item Get a move from another playbook
\item Get an Advanced Voiced move
}

\renewcommand{\StatsSpaceAdjust}{3em}
\renewcommand{\MoveExplanation}{Voiced gets the \textbf{Charming Voice} move, and 2 other moves of your choice.}

\renewcommand{\Moves}{
  \setlength\itemsep{-.25em}
  \DEFAULTMOVE{Charming Voice}{When you \TRIGGER{Sell a Lie} using your voice to do so, you may roll +Without instead of +Dynamic}


\MOVE{Voice in the Wind}{When you \TRIGGER{speak across boundaries} that would otherwise make communication impossible, you are heard.}

\MOVE{Power Vested in Me}{When you \TRIGGER{speak as the voice of a significant or powerful group}, and with their full weight and authority, roll +Static. On a 10+ those you are speaking to will take you at your word, on a 7-9, they will need some proof or assurances first.}

\MOVE{Arresting Voice}{When you \TRIGGER{use your voice to deliver a message that is both powerful and captivating}, roll +Without. On a 10+, your audience is frozen, unable to do anything other than to continue listening until you finish. On a 7-9, they are likewise frozen, but you must not take any action other than to continue delivering your message, or the spell will be broken.}

\MOVE{The Voice of Experience}{When you \TRIGGER{have been here before}, give advice on a course of action and roll +Dynamic, -1 if Tethered. On a 7-9, take +1 forward when following the plan. On a 10+, additionally everyone who follows the plan marks experience.}

}
\renewcommand{\SpecialMoveSpacing}{20em}
\renewcommand{\SpecialMove}{you may tell them a secret about yourself. If you do, they will respond with a secret about themselves.}

\renewcommand{\Paradigms}{
  \PARADIGM{I am a Voice in the Chorus}{Words spoken which become Truth, divine insight  }\
  
           {(choose one) Harmful magic, dissonant magic  }\
		   
           {(choose one) silent magic, magic done alone}
		   
  \PARADIGM{Spirit Whisperer}{The breath of life, soothing magic, transcending barriers  }\
  
           {(choose one) Loud magic, wards, entropic magic  }\
		   
           {(choose one) Magic without spirits, silent magic, my magic must be expressed as a request, my magic depends on a willing spirit}
		   
  \PARADIGM{Music is the language of the Universe}{Regular rhythms, variations on a theme, harmonious magic, cosmic vibrations  }\
  
           {(choose one) Chaotic magic, countermagic, singular effects  }\
		   
           {(choose one) Soundless magic, emotionless magic, my magic must be a song}
		   
}
\renewcommand{\PaneSix}{\Description

\GearSection
}

\begin{document}

\PLAYBOOK

\end{document}