% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Wayfarer}
\renewcommand{\Picture}{Wayfarer-new}
\renewcommand{\Description}{There are many who travel the world in this day and age, and many fewer who travel where you do. The journey of a thousand miles begins with you.
}
\renewcommand{\Names}{Roland, Isobel, Amelia, Karma, Daniel, Celina, Jamie, Gabriel, Christopher, Morgan, Laurie, David, Cara, Trina, Corwin}
\renewcommand{\Trivialized}{{\small Because I couldn't keep up, because of my attitude, because the world isn't accessible, \BLANK}}
\renewcommand{\Questioned}{{\small Because I don't care, because people started noticing me, Because I see things as they really are, \BLANK}}
\renewcommand{\Hunted}{{\small Because I run, because I break the Rules, for what I know, \BLANK}}

\renewcommand{\Eyes}{spirited eyes, tender eyes, distant eyes, daring eyes, wandering eyes, secretive eyes}
\renewcommand{\Faces}{stolid face, eager face, weathered face, angular face, weary face, covered face}
\renewcommand{\Bodies}{vibrant body, waifish body, hardened body, fluid body, mousy body, weird body \BLANK}
\renewcommand{\Clothes}{tattered clothes, soiled clothes, crisp clothes, foreign clothes, comfortable clothes, tough clothes}
\renewcommand{\Auras}{tireless aura, vital aura, capricious aura, eccentric aura, boisterous aura, nondescript aura}

\renewcommand{\HomeAnchorItems}{
\item My well-maintained but tempermental conversion van
\item  My house that always seems to need repair
\item  A well-used tent and backpacking gear
}
\renewcommand{\ConnectionAnchorItems}{
\item Iris, who will be my legacy
\item  My family
\item  Devin, my childhood chaplin
}
\renewcommand{\MemoryAnchorItems}{
\item My well-polished Harley
\item  My tattered, empty diary
\item  My collection of smoothed stones
}
\renewcommand{\Gear}{
\item No Savings

\item Choose a means of getting around: My well-cared-for motorcycle; A walking staff and good pair of boots; The latest in a long series of cars, not yet on its last legs.

\item Choose a way of protecting yourself: A pet dog, your loyal traveling companion; Enough hidden knives to arm a small gang; A pistol with a hidden holster

\item Choose a curiosity: A map to somewhere you’ll need to go again; A spirit totem that isn't sure it accepts you as its owner; The latest in amateur radio technology

}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Pick a new Wayfarer Move
\item Gain +1 Static (Max Static +1)
\item Gain +1 Without (max Without +3)
\item Gain +1 Within (max Within +3)
\item Gain +1 Entropic (max Entropic +2)
}
\renewcommand{\SpecialAdvancements}{
\item Pick a new Wayfarer move
\item When using Step Sideways, always choose +1 option, even on a miss
\item Pick a playbook move from another playbook
\item Pick a playbook move from another playbook
\item Gain +1 Dynamic (max Dynamic +3)
\item Get an Advanced Wayfarer Move
}
\renewcommand{\MoveExplanation}{The Wayfarer gets the \textbf{Step Sideways} move, and 2 other moves of your choice.}
\renewcommand{\MoveSpacing}{0em}
\renewcommand{\Moves}{
  \DEFAULTMOVE{Step Sideways}{When you \TRIGGER{seek a path to step sideways and travel to someplace new}, roll +Entropic. On a 10+ choose 4, on a 7-9 choose 2.  \vspace{-.5em}
\begin{itemize}
\setlength\itemsep{-.5em}
\item You get where you meant to go, no funny business.
\item You arrive promptly.
\item You arrive unharmed.
\item You remember the path, so you can travel it again.
\item You can safely and easily return.\end{itemize}}

\MOVE{Chance Meetings}{When you \TRIGGER{meet an important stranger} (your choice) in your travels, roll +Dynamic. On a 10+ choose one, on a 7-9 the MC will choose one.
\begin{itemize}
\setlength\itemsep{-.5em}
\item They tell you something useful and true.
\item They give you something that is potentially useful.
\item They have something of great value to you.
\item You have something of great value to them, and you know it.\end{itemize}}

\MOVE{Sixth Sense}{When you \TRIGGER{travel along a path before it happens}, roll +Within, and see a vision of possible futures. On a 10+, tell the MC what you sense, they may add to it. On a 7-9, the MC will tell you what you sense, and two possible interpretations.}

\MOVE{Parkour}{When you \TRIGGER{Outfox in an urban jungle}, on a 12+ you additionally hold 3. You can spend your hold one for one to:
\begin{itemize}
\setlength\itemsep{-.5em}
\item Take +1 forward on an additional Outfox roll
\item Take +1 forward to keeping your head down
\item Treat your skills as something a sleeper wants for Use a Sleeper\end{itemize}}

\MOVE{Any Port in a Storm}{When you \TRIGGER{find yourself in an unwelcoming situation}, roll +Dynamic. On a 10+, tell the MC what you recognize as familiar and how that helps you. On a 7-9, the MC will tell you.}

\MOVE{The Soul of an Explorer}{When you \TRIGGER{seek out or find an entirely new experience}, roll +Dynamic. On a hit, you learn something, mark experience. On a 10+, you find something that makes it easier, safer, or more enjoyable, the MC will tell you what.}

}



\renewcommand{\SpecialMoveSpacing}{0em}
\renewcommand{\SpecialMove}{roll +Within. On a 10+, once, you can step sideways to this person as if they were a place you’ve never been before. On a 7-9, you see each other in a new light, you each pick one from the Chance Meetings list for the other. On a 6-, take -1 ongoing until you prove they haven't chained you down or anything.}

\renewcommand{\Paradigms}{
  \PARADIGM{All people are connected, all people affect one another}{Symparthy magic, travel magic  }\
  
           {(choose one) Creation, permanent effects  }\
		   
           {(choose one) Binding magic, magic that prevents movement}
		   
  \PARADIGM{I have one foot in the spirit world}{Travel between worlds, opening things, spirit magic  }\
  
           {(choose one) Static magic, abstract magic  }\
		   
           {(choose one) Magic that uses physical objects, stationary magic}
		   
}

\renewcommand{\PaneSix}{\Description

\GearSection
}

\begin{document}

\PLAYBOOK

\end{document}