% -*- Mode: latex -*-
\input{moves.tex}

\chead{\titlefont\Huge\textbf{The Basic Moves}}

\begin{document}
\begin{multicols}{3}

  \begin{move}
    When you  \TRIGGER{assert your Paradigm},  over another Mage’s, roll +Static (-1 if Tethered). On a 10+, hold 3, or on a 7-9, hold 1. You can spend your hold 1 for 1 to:

    \begin{itemize}
      \setlength\itemsep{-.5em}
    \item Have them mark experience (if an NPC, they comply with a reasonable request)
    \item Give them a +1 or -1 on their next roll (if an NPC, enhance or counter their next use of magic)
    \item Cause their current Discord to backlash. 
    \item Offer yourself as an Inspiration to their character (they do not need to accept)
    \end{itemize}
    On a miss, they hold 1 against you, on the same terms.


  \end{move}

  \SEPARATOR

  \begin{move}
    When you  \TRIGGER{impress a lusus naturae with a feat of magic in order to sway them,} they will expect something in return. Roll +Without (-1 if Tethered). On a 10+, they will do what you want if you promise to do it. On a 7-9 they may choose to instead:

    \begin{itemize}
    \item Give you something else they think you want or need
    \item Make themselves scarce
    \item Require you to fulfill the promise before they help.
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
    When you  \TRIGGER{use a sleeper} for your own ends, you must first present something they want. Roll +Without. On a 10+, they will do what you want to the best of their abilities, but on a 7-9, they’ll need proof that they’ll get what they want, or they’ll need it before they do anything for you.

  \end{move}

  \SEPARATOR

  \begin{move}
    When you  \TRIGGER{help or hinder another PC}, roll +Anchors. On a 10+ they get a +1 or -2 to their roll, your choice. On a 7-9 they still get the bonus or penalty, but you open yourself to cost, danger, or retribution. If they are doing magic that is Aligned to your Paradigm, you may instead have them treat the result as one category higher or lower.

  \end{move}

  \columnbreak
    
  \begin{move}
     \TRIGGER{}

  \end{move}

  \vspace{1em}
  
  \SEPARATOR

  \begin{move}
    When you  \TRIGGER{outfox, outpace, or outmaneuver} to avoid a danger, name your gambit and roll +Dynamic. On a 10+, you pull it off, just as described. On a 7-9 choose 1:

    \begin{itemize}
      \setlength\itemsep{0em}
    \item you overextend yourself in the process
    \item you come away with something missing
    \item someone else is drawn in.
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
     \TRIGGER{}
    \begin{itemize}
      \setlength\itemsep{0em}
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
     \TRIGGER{}
    \begin{itemize}
      \setlength\itemsep{0em}
    \end{itemize}

  \end{move}

  \SEPARATOR

  \begin{move}
     \TRIGGER{}
  \end{move}

  \columnbreak
  
  \begin{move}
      \TRIGGER{}
    \begin{itemize}
      \setlength\itemsep{0em}
    \end{itemize}
    \end{itemize}
  \end{move}

  \SEPARATOR

  \begin{move}
     \TRIGGER{}
    \begin{itemize}
      \setlength\itemsep{0em}
    \end{itemize}

  \end{move}

\end{multicols}
\end{document}