% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Pious}
\renewcommand{\Picture}{Pious-new}
\renewcommand{\Description}{You know the true meaning of sacrifice. It isn't something dramatic or grandiose, sometimes it just means going without sleep so you can stake out the fields that cows keep disappearing from. There's Something larger than just you, and choosing that over your own needs, that's sacrifice.
}
\renewcommand{\Names}{Joan, Ether, Miranda, Brother Wilhelm, Francis, Emira, Marja, Ingrid, Bernard, Rishi, Sister Eliza}
\renewcommand{\Trivialized}{Because of my beliefs, because of my family ties, because I couldn't keep up, \BLANK}
\renewcommand{\Questioned}{Because I keep screwing up, beccause I can't keep my mouth shut, because of my anger, \BLANK}
\renewcommand{\Hunted}{Because I break the Rules, for my beliefs, for the Truth, \BLANK}

\renewcommand{\Eyes}{caring eyes, quiet eyes, intense eyes, small eyes, inspired eyes, hard eyes}
\renewcommand{\Faces}{youthful face, lined face, sharp face, round face, marred face, open face}
\renewcommand{\Bodies}{hard body, sallow body, frail body, large body \BLANK}
\renewcommand{\Clothes}{orderly clothes, homespun clothes, conservative clothes, starched clothes}
\renewcommand{\Auras}{peaceful aura, driven aura, flowing aura, tight-fitting aura, hidden aura}

\renewcommand{\HomeAnchorItems}{
\item The alley behind the best Chilean restaurant in the city
\item  My cramped apartment downtown
\item  My cared-for house with a welcome mat out front
}
\renewcommand{\ConnectionAnchorItems}{
\item Kell, my heart's delight
\item  My widowed sister-in-law
}
\renewcommand{\MemoryAnchorItems}{
\item My wooden rose, a gift from my first love
\item  My dog-eared holy text
}
\renewcommand{\Gear}{
\item 1 Savings

\item Choose a way of strengthening bonds: An altar, complete with spiritual accoutrements; A branch from the Oath Tree; A table at the best restaurant in this half of the city; A hand-woven prayer mat.

\item Choose a ritual supply that you have a small stock of: Holy Water; Incense from a far-away place; Rare herbs; Preserved animal bones; Graveyard dirt; Specially prepared ink and paper

\item Choose a creature comfort: A hotel of the month club membership; A bottle of 18 year Macallan; A luxurious bathrobe and slippers; A set of high-end noise-cancelling headphone

}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Charm (Maximum Charm +3)
\item Gain +1 Grace (Maximum Grace +2)
\item Gain +1 Will (Maximum Will +2)
\item Gain +1 Wits (Maximum Wits +2)
\item Get a new Pious move
}
\renewcommand{\SpecialAdvancements}{
\item t a new Pious move
\item Get a new Pious move
\item Choose a new option for your Place of Power
\item Choose a new option for your Place of Power
\item Get a playbook move from another book
\item Get a playbook move from another book
\item Get an Advanced Pious Move
}

\renewcommand{\MoveExplanation}{The Pious gets the \textbf{Vows} move, and 2 other moves of your choice.}
\renewcommand{\Moves}{
  \setlength\itemsep{-.25em}
  \DEFAULTMOVE{Vows}{When you \TRIGGER{Eschew Mortal Comfort in favor of aiding someone else}, roll +Static. On a 10+ hold 3, on a 7-9 hold 1. Spend your hold 1-for-1 to declare someone involved in a situation owes you a small favor for past help.}


\MOVE{Listen to the Celestial Chorus}{When you \TRIGGER{tune in to the voices of the universe}, sometimes they will have something helpful to say. Roll +Static. On a hit you may ask questions from the below list, the MC will answer truthfully. On a 10+ ask 3, on a 7-9 ask 1.
\begin{itemize}
\setlength\itemsep{-.5em}
\item Who here has the most potential?
\item Who can I trust?
\item What am I not seeing?
\item Who is telling the truth?\end{itemize}}

\MOVE{Sanctuary}{You have access to a Place of Power, a safe haven against things that would harm servants of your Path.\TRIGGER{}}

\MOVE{Clarity of Purpose}{When you \TRIGGER{talk someone through a Restriction on their Paradigm}, they remove that Restriction.}

\MOVE{Exorcism}{When you \TRIGGER{banish an inhabiting spirit} roll +Dynamic. On a 10+ choose 1, on a 7-9 choose 2:
\begin{itemize}
\setlength\itemsep{-.5em}
\item You expose yourself to possession
\item The spirit is ill-disposed towards you
\item The inhabited subject is harmed.\end{itemize}}

\MOVE{Holy Avenger}{You have a weapon, enchanted and attuned to your beliefs. When you \TRIGGER{use it to bring death}, justify why this is necessary, and roll +Entropic. On a hit, you may incapacitate or kill any one opponent on the battlefield. On a 7-9, they have a chance to react first, but can't stop you. On a 6-, they were prepared. Sucks to be you.}

}

\renewcommand{\SpecialMoveSpacing}{10em}
\renewcommand{\SpecialMove}{roll +nothing. On a 10+, either you or they lose one Discord, their choice. On a 7-9, they choose whether to transfer one Discord from you to them or from them to you.}

\renewcommand{\Paradigms}{
  \PARADIGM{All is One and the One is All}{Pattern magic, cooperative magic  }\
  
           {(choose one) Selfish magic, magic that divides  }\
		   
           {(choose one) Magic without Faith, magic that doesn't involve people}
		   
  \PARADIGM{I am the New Prophet}{Visions of the Future, Forging a Destiny  }\
  
           {(choose one) Things at rest, Abjuration  }\
		   
           {(choose one) Changing the Future you Know, Hiding the Truth}
		   
}

\renewcommand{\PaneSix}{\Description

  \SECTION{Place of Power:}
  
  First, pick a facade:	
  \begin{itemize}
  \item Place of Worship
  \item Forested Grove
  \item Basement Laboratory
  \item Old Log Cabin
  \item Wishing Well
  \item Ancestral Mausoleum
  \item Natural Spring
  \end{itemize}
    
  Then pick up to 1 Strength: 
+warded, 
+accorded ground, 
+famous, 
+private, 
+unique, 
+awakened spirit


  Pick at least 1 Weakness: 
+inaccessible, 
+obvious, 
+public, 
+tainted 
+exposed, 
+business hours, 
+cramped


  A Ritual performed here will never (choose 1):
  \begin{itemize}
  \item Need a certain object
  \item Cause everyone involved to Backlash
  \item Need extra time
  \end{itemize}

  \GearSection
}

\begin{document}

\PLAYBOOK

\end{document}