% -*- Mode: latex -*-
\input{playbook.tex}

\renewcommand{\Name}{Tech Adept}
\renewcommand{\Picture}{Tech-Adept-new}
\renewcommand{\Description}{Most people think magic and tech are incompatible, but you know better. You prefer to think of them as peanut butter and chocolate. And you're the sweet sweet mix.
}
\renewcommand{\Names}{Jeremy, Kix, Sonya, B3ll, Doran, Starter, TK, Foto, Liza, The Law, Dodge, Ophelia, Tarvek, Fr0st, Amanda}
\renewcommand{\Trivialized}{Because of my obsession, because of my transgressions, because I was uneducated   \BLANK}
\renewcommand{\Questioned}{Because I'm holding back, because I don't care, because I don't know how to fit in   \BLANK}
\renewcommand{\Hunted}{For my talents, because I get framed, because I antagonize \BLANK}

\renewcommand{\Eyes}{cocky eyes, darting eyes, vacant eyes, lively eyes, emotionless eyes}
\renewcommand{\Faces}{driven face, stony face, fervent face, steady face, broad face, impassive face}
\renewcommand{\Bodies}{jumpy body, gangling body, striking body, burly body, awkward body \BLANK}
\renewcommand{\Clothes}{otective clothes}
\renewcommand{\Auras}{ra}

\renewcommand{\HomeAnchorItems}{
\item A squat without running water
\item  My nicely decorated apartment, walking distance from public transit
\item  A room-share start-up pilot program
}
\renewcommand{\ConnectionAnchorItems}{
\item My only uncle, Avi
\item  Zeke, from my virtual community
}
\renewcommand{\MemoryAnchorItems}{
\item The tree-house I built with \BLANK
\item  My frist hand-held console
\item  My mint copy of \BLANK
\item  My High School Diploma, which I almost had to forge
}
\renewcommand{\Gear}{
\item 2 Savings

\item Choose a signature toolset: My souped-up computer; a set of scripts and daemons that I can reach from anywhere with an internet connection; All the meters, connectors, and components I could need.

\item Choose something you've made: A full home automation system; An Internet watchdog to keep you informed; A weapon using Consensus-defying energies.

}
\renewcommand{\StatsSpaceAdjust}{0em}
\renewcommand{\BasicAdvancements}{
\item Gain +1 Charm (Max Charm+2)
\item Gain +1 Grace (Max Grace +2)
\item Gain +1 Body (Max Body +2)
\item Gain a new Tech-Adept move
\item Gain a new Tech-Adept move
}
\renewcommand{\SpecialAdvancements}{
\item Gain +1 Will (Max Will +2)
\item Gain a new Tech-Adept move
\item Pick a playbook move from another playbook
\item Get an Advanced Tech-Adept Move
\item Get an Advanced Tech-Adept Move
}
\renewcommand{\MoveExplanation}{The Tech Adept gets the \textbf{Universal Programmer} move, and 2 other moves of your choice.}
\renewcommand{\MoveSpacing}{-.25em}
\renewcommand{\Moves}{
  \DEFAULTMOVE{Universal Programmer}{When you \TRIGGER{make a new piece of equipment}, roll +Dynamic. On a hit you make it. On a 10+, it works and keeps working. On a 7-9, it will only last for the scene. In either case, choose a quirk:
\begin{itemize}
\setlength\itemsep{-.5em}
\item The device works much more slowly than expected
\item The device requires more of a resource than expected
\item The device has a side effect when used\end{itemize}}

\MOVE{Read the Web of Fate}{When you \TRIGGER{enter the virtual world to Read the Web of Fate}, roll +Without. On a hit, you can determine the degrees of separation between two objects or people. On a 10+, you can also get a general idea of the path between them.}

\MOVE{Ghost in the Machine}{When you \TRIGGER{enter the Virtual World physically}, you may bring other willing Mages along, and exit at any terminal you can find.}

\MOVE{Things Speak}{When you examine an interesting technological or magical object, roll +Without. On a 10+, you may ask up to 3 of the following questions, on a 7-9, ask 1.\TRIGGER{}
\begin{itemize}
\setlength\itemsep{-.5em}
\item What strong emotions have been most recently associated with this?
\item What’s wrong with this, and how might I fix it?
\item How frequently has this been handled?
\item Where did this come from?
\item How might this be dangerous?
\item Who designed this?\end{itemize}}

\MOVE{Percussive Maintenance}{When you \TRIGGER{impose your will on a machine}, roll +Entropic. It works better. On a 10+, tell the MC how. On a 7-9, the MC will tell you how. On a 6-, the MC will tell you how, and why this is terrible for you.}

}
\renewcommand{\SpecialMoveSpacing}{9em}
\renewcommand{\SpecialMove}{they speak to you as if they were an interesting technological or magical object (whether or not you have the move). Treat it as rolling a 10+ and ask up to 3 questions from the list. If you ask more than 1 question, you speak back to them in the same way, and they may ask up to 3 questions of the same list.}

\renewcommand{\Paradigms}{
  \PARADIGM{Reality has an API}{Changing a signle variable, magic done from a terminal  }\
  
           {(choose this one) Living things  }\
		   
           {(choose one) Unplanned magic, magic not done from a terminal}
		   
  \PARADIGM{My Own \textit{Theory of Everything}}{The physical world, repeated magic}\
  
           {(choose one) Magic not of the physical world, magic that violates the Law of Entropy  }\
		   
           {(choose this one) Magic without technological accountrements}
		   
}

\renewcommand{\PaneFiveSpace}{50em}

\renewcommand{\PaneSix}{\Description

\GearSection}

\begin{document}

\PLAYBOOK

\end{document}